Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-13 automatica/paper.tex
sec 5

\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
%
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
\Rightarrow \phi_\mathit{init}^{K}$$
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.

@@

We recall a technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of
the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we
transform this problem into a one-step solution.  We first change the
problem statement by means of acceleration into
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and further define new model semantics and corresponding set: 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
In this work we use an extension of the abstract acceleration model for
continuous time. For this reason we must first look at the accelerationm of continuous time dynamics.

@@

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in
order to synthesize $\mat{K}$, we must be able to ensure that
certain properties of the plant hold at any given point in time.  In order
to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
$t=T$.

@@

\textcolor{red}{Elizabeth: this section needs to be updated to describe about floating-point arithmetic.}

The models we consider have two sources of error that are due to numerical  
representation.  The first is the numerical error introduced by the
fixed-point numbers employed to model the plant, i.e., to represent the
plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
introduced by the digital controller, which performs operations on
fixed-point numbers.  In this section we outline the notation for the
fixed-point representation of numbers, and briefly describe the errors
introduced.  A~formal discussion is in
%Appendix~\ref{appendix:numerical_errors}.

>>>>

\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
%
\textcolor{red}{[these specifications are (wrongly) introduced only in a later part of the manuscript!]}
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
\Rightarrow \phi_\mathit{init}^{K}$$
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.

@@

We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key in this work for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
\textcolor{red}{[we should use the notations (with the `d' subscript) in the Preliminaries section.]}
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of
the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we
transform this problem into a one-step solution.  We first change the
problem statement by means of acceleration into
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and further define new model semantics and corresponding set: 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
In this work we use an extension of the abstract acceleration model for
continuous time. 
% and  For this reason we must first look at the acceleration of continuous-time dynamics.

@@

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in
order to synthesize $\mat{K}$, we must be able to ensure that
certain properties \textcolor{red}{[unknown because undefined at this point \ldots]} of the plant hold at any given point in time.  In order
to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
$t=T$.

@@

\textcolor{red}{Elizabeth: this section needs to be updated to describe floating-point arithmetics.}

The models we consider have two sources of error that are due to numerical representations.  
The first is the numerical error introduced by the
fixed-point numbers employed to model the plant, i.e., to represent the
plant dynamics $A_d$, $B_d$ and $x_k$.  The second is the quantization error
introduced by the digital controller, which performs operations on
fixed-point numbers.  
\textcolor{red}{[what about the DAC/ADC errors?]}
In this section we outline the notation for the
fixed-point representation of numbers, and briefly describe the errors
introduced.  A~formal discussion is in
%Appendix~\ref{appendix:numerical_errors}.
